\vfill World of Warcraft's New Way to Get You Hooked

### 2013-04-04 paper.tex
7. Deleted and summarized Pearce quote.

During a panel at D.I.C.E. 2012 \cite{DICEInterview} that included Mike Epps, President of Epic Games, Ted Price, CEO and Founder of Insomniac Games, and Frank Pearce, current VP of product development and one of the three founders of Blizzard, Frank Pearce had this to say about World of Warcraft:
\begin{quote}
[W]e hear stories all the time, in fact right when we were walking out for the break, someone came up to me and said ``I just want you to know, I'm in this industry because I suffered a back injury and I spent six years playing Warcraft and decided I wanted to get into the games industry.'' We get letters from players all the time that can't experience the real world in the way that they would like to because of physical limitations and can live a completely free experience in a game like World of Warcraft.
\end{quote}
Blizzard Entertainment is doing so many people a service that they actually receive letters thanking them for making such an immersive experience.

>>>>

During a panel at D.I.C.E. 2012 \cite{DICEInterview} that included Mike Epps, President of Epic Games, Ted Price, CEO and Founder of Insomniac Games, and Frank Pearce, current VP of product development and one of the three founders of Blizzard, Frank Pearce discussed a letter he received from a fan who had a disability and found comfort in World of Warcraft. He went on to say that Blizzard Entertainment is doing so many people a service that they actually receive letters thanking them for making such an immersive experience. \cite{DICEInterview}
